The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-20 paper/ms.tex

Many evolutionary processes are expected to occur over the lives of
stars and exoplanets; it would be interesting to statistically observe
these changes as functions of time.
However, since most dwarf star properties do not appreciably change
until the stars evolve off the main sequence, creative approaches must
be used to infer stellar ages \citep{soderblom_ages_2010}.
In the study of exoplanets, one approach beginning to bear fruit
is to search for planets in open clusters and moving groups.
The ages of these stellar ensembles are inferred through isochrone
analyses, and are typically most constrained by the location of the
main-sequence turnoff and/or the red giant branch (CITE IF TRUE).
Once calibrated, gyrochronology can also be used to verify
the age of a stellar ensemble \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered around these cluster stars are then
assumed to equal those of the star.

The first planets in open clusters were detected through radial
velocity (RV) measurements of evolved stars in the Hyades
\citep{Sato_et_al_2007}, and in NGC~2423 \citep{lovis_mayor_2007}.
Subsequent spectroscopic searches in Praesepe led to the detection of
the first hot Jupiters in a cluster \citep{Quinn_et_al_2012}, and also
the first multi-planet system \citep{Malavolta_et_al_2016}.
The youngest RV detections have come from surveys of T Tauri stars in the
Taurus star-forming region, which showed signals of the hot Jupiter
\citep[V830~Tau~b][]{donati_hj_2016} and of a giant planet on a 9-day orbit
\citep[CI~Tau~b][]{johns-krull_candidate_2016,flagg_co_2019}.
A final RV survey of note was conducted by
\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
years.  They reported detections of three hot Jupiters around main
sequence stars, and of one giant planet around an evolved star.

The transit method was slow to catch up, despite deep searches of
M~37 by \citet{hartman_MMT_IV_2009}, as well as
searches of nine young clusters in the solar neighborhood
by the Monitor project
\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
While these studies led to valuable measurements of stellar
rotation \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
the discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
\citep{irwin_monitor_PMSEB_2007}, no planet in open clusters were
uncovered.  Transit searches in globular clusters were similarly met
with null results \citep{gilliland_lack_2000,
weldrake_searching_2006}.

Kepler \citep{borucki_kepler_2010} was the first project to observe a
sufficient number of stars for long enough and with sufficient
precision to detect transiting planets in open clusters:  Kepler-66b
and 67b, in the gigayear-old NGC~6811 \citep{Meibom_et_al_2013}.
Though a broken reaction wheel ended the prime Kepler mission, the
repurposed K2 mission \citep{howell_k2_2014} switched between
fields along the ecliptic every quarter-year, and was able to observe
far more clusters and young stars.
In particular, K2's detections through its surveys of the Pleiades,
Hyades, Praesepe, and Upper Sco were a major inspiration for the
present work.

K2-25b, discovered in the Hyades, had a radius ($3.43\,R_\oplus$) that was
larger than older Kepler planets at similar insolation levels
\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that the
planet is contracting, or losing its atmosphere (e.g., CITE).  The
super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper Sco,
showed that at least some close-in planets must form within about 10 Myr,
excluding long-timescale migration as an explanation for its origin
\citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries included six
transiting planets in Praesepe \citep{obermeier_k2_2016,Mann_et_al_2017}, a
long-period candidate super-Earth in the Hyades
\citep{vanderburg_zeitVII_2018}, the three-planet K2-136 system in the Hyades
\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and also the
two-planet system K2-264 in Praesepe
\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  A final recent
K2 detection is of a Jupiter-sized planet orbiting every 24 days around V1298
Tau \citep{david_v1298_2019}.

Clearly, a significant amount of effort has been and continues to be
devoted towards the discovery and characterization of planets around
young stars.
Sometimes, cluster membership may not even be necessary, if a star's
youth can be inferred based on a combination of rotation, activity,
and kinematic indicators \citep[{e.g.}, K2-233][]{david_k2-233_2018}.
To investigate demographics in time, the detection sensitivities and
reliabilities of these searchers need to be calibrated, likely with a
machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.
A separate requirement for population studies to be statistically
robust, imposed by the geometric rarity of transits, is that many tens
of thousands of stars with known ages must be monitored at high
precision.

The TESS mission \citep{ricker_transiting_2015} holds the promise to
deliver the most homogeneous and comprehensive cluster photometric
survey in history.  Based on the cluster membership database of
\citet{Kharchenko_et_al_2013} and the TESS apparent magnitude
calculator of \citet{Jaffe_Barclay_2017}, we estimated that $\approx
2\times10^5$ cluster members brighter than $T=16$ will be observed in
the full-frame images over the first two years of TESS observations.
The actual number may be even larger, as cluster membership catalogs
are by no means complete, even at these relatively bright magnitudes.
For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
discovered a few tens of previously undetected open clusters in
the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
fortuitously discovered 60 open clusters as well; however a
homogeneous all-sky search with Gaia data has yet to be performed.

>>>>

Many evolutionary processes are expected to occur over the lives of
stars and exoplanets; it would be interesting to statistically observe
these changes as functions of time.  However, since most dwarf star
properties do not appreciably change until the stars evolve off the
main sequence, creative approaches must be used to infer stellar ages
\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
the study of exoplanets is to search for planets in coeval groups of
stars, {\it i.e.} in clusters.  This includes the open clusters of
yore, as well as the moving groups and stellar associations that began
to be uncovered in the late 1990s \citep{zuckerman_young_2004}.  The
ages of these stellar ensembles are inferred through isochrone
analyses on color-magnitude diagrams, using an appropriate combination
main-sequence turnoff locations, pre-MS turnon locations, and/or MS
isochrones for the known cluster members \citep[{\it e.g.},][Section
3.4.3]{kharchenko_global_2012}.  Once calibrated, gyrochronology can
also be used to verify the age of a stellar ensemble \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered in these cluster stars are then
assumed to equal the age of the larger stellar ensemble.

The first planets in open clusters were detected through radial
velocity (RV) measurements of evolved stars in the Hyades
and NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
Subsequent spectroscopic searches in Praesepe led to the detection of
the first hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also
the first multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
The youngest RV detections have come from surveys of T Tauri stars in the
Taurus star-forming region, which showed signals of the hot Jupiter
\citep[V830~Tau~b][]{donati_hj_2016} and of a giant planet on a 9-day orbit
\citep[CI~Tau~b][]{johns-krull_candidate_2016,flagg_co_2019}.
A final RV survey of note was conducted by
\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
years.  They reported detections of three hot Jupiters around main
sequence stars, and of one giant planet around an evolved star.

The transit method was comparatively slow to catch up, despite deep
searches of M~37 by \citet{hartman_MMT_IV_2009}, as well as searches
of nine young clusters in the solar neighborhood by the Monitor
project
\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
While these studies led to valuable measurements of stellar rotation
periods \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
the discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
\citep{irwin_monitor_PMSEB_2007}, no transiting planets in open
clusters were found.  Transit searches in globular clusters were
similarly met with null results \citep{gilliland_lack_2000,
weldrake_searching_2006}.

Kepler \citep{borucki_kepler_2010} observed enough stars for long
enough and with sufficient precision to detect transiting planets in
open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
switched between fields along the ecliptic every quarter-year, and was
able to observe far more clusters and young stars.  The resulting
discoveries made by K2 through its surveys of the Pleiades, Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work.

K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
is larger than older Kepler planets at similar insolation levels
\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
the planet is contracting, or losing its atmosphere (e.g., CITE).  The
super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
Sco, showed that at least some close-in planets must form within about
10 Myr, excluding long-timescale migration as an explanation for its
origin \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
included six transiting planets in Praesepe
\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
three-planet K2-136 system in the Hyades
\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
also the two-planet system K2-264 in Praesepe
\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
recently been a detection by K2 of a Jupiter-sized planet orbiting
every 24 days around V1298~Tau \citep{david_v1298_2019}.

A significant amount of effort continues to be devoted towards the
discovery and characterization of planets around young stars.
Sometimes, cluster membership may not even be necessary, if a star's
youth can be inferred from combined rotation, activity, and kinematic
indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
investigate demographics in time, the detection sensitivities and
reliabilities of these searchers need to be calibrated, likely with a
machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
separate requirement for population studies to be statistically
robust, imposed by the geometric rarity of transits, is that many tens
of thousands of stars with known ages must be monitored at high
precision.

%FIXME probably rework the following two paragraphs?
The TESS mission \citep{ricker_transiting_2015} holds the promise to
deliver the most homogeneous and comprehensive cluster photometric
survey in history.  As an order of magnitude estimate, the 
\citet{Kharchenko_et_al_2013} combined with the TESS apparent magnitude
calculator of \citet{Jaffe_Barclay_2017} indicated that $\approx
2\times10^5$ cluster members brighter than $T=16$ will be observed in
the full-frame images over the first two years of TESS observations.
The actual number will be larger, as cluster membership catalogs
are not yet complete, even at these relatively bright magnitudes
\citep[{\it e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
% For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
% discovered a few tens of previously undetected open clusters in
% the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
% fortuitously discovered 60 open clusters as well; however a
% homogeneous all-sky search with Gaia data has yet to be performed.

For moving groups and stellar assocations, it is typically a simple thing to do
aperture photometry.  A number of promising targets from TESS are in various
stages of follow-up for this, notably DS Tuc Ab (TOI 200,
\citealt{benatti_dstuc_2019}, Newton+2019), as well as TOI-450 and TOI-451.
This is good, and these will remain benchmark systems because they are close
and bright.  However, to do statistics, we need more stars -- we need to
investigate the full range of cluster properties (densities, ages,
metallicities).  This motivates the need to go crowded.
